R for Clinical Study Reports and Submission

### 2021-09-17 intro.Rmd
Update intro.Rmd

The workflow around an R package can also improve 
the tractability and reproducibility for an analysis project [@marwick2018packaging].

>>>>

The workflow around an R package can also improve 
the traceability and reproducibility for an analysis project [@marwick2018packaging].

We will revisit folder structure when we discuss project management for a clinical trail project.
